\problemname{Reindeer \& Elves}

You're about to go home for Christmas, but you've been urgently paged to the North Pole to
solve a dilemma. 

"Every year," Mrs. Claus says, "in Santa's workshop, there are $r$ reindeer and $e$ elves that 
work together in harmony."

However, she explains, this year the reindeer and elves have been quabbling amongst themselves, 
and now the reindeer claim that they will only work with certain elves. Unfortunately, even 
whilst working their tiffs continue, and so the reindeer's preferences change by the hour. 
For each hour, a reindeer will only work with one elf out of its preferred elves. In turn, 
an elf can work with at most one reindeer each hour. And both must work in pairs, which will allow
them to make and deliver up to 25 gifts per hour. 

Given a gift quota $g$, determine whether this quota can be met based on the given reindeer schedule
and their preferred elves. Note that not all reindeer are available at every hour. For example, 
$r_1$ may be available at hours 1, 2, 3, 4 and $r_2$ may be available at hours 1, 3.

\section*{Input}

The first line of input contains 3 integers $r, e, g$ ($1 \leq r \leq 9$ and $1 \leq e \leq 25\,000$ 
and $0 \leq g \leq 18\,446\,744\,073\,709\,551\,615$) as defined in the problem. Then, for the next $r$ 
lines, there is a $r_i$ ($1 \leq i \leq 9$) differentiating the reindeer. On the next hours $h$ lines, for each 
$r_i$, the first integer is $h$, and the next integer is some quantity of $e_j$ ($1 \leq j \leq 25\,000$), 
space separated, that a reindeer can work with in that hour. A separate line containing 0 marks the end of a 
reindeer's preferences list.

\section*{Output}

Output "possible" if the gift quota can be met, or "impossible" if not. 